\documentclass[a4paper]{report}
\usepackage[table]{xcolor}
\usepackage[top=3cm, bottom=3cm, left=4cm, right=4cm]{geometry}
\usepackage{graphicx}
\usepackage{svg}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[parfill]{parskip}
\usepackage[font={small,it}]{caption}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{quoting}

% Biliography
\usepackage[sectionbib, numbers]{natbib}
\usepackage{chapterbib}

% Colors 
\definecolor{aux_pink}{HTML}{9F1F79}
\definecolor{aux_green}{HTML}{006561}

% Headers and footers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{\leftmark}
\fancyfoot{}
\fancyfoot[C]{\thepage}

% Example box
\usepackage{tcolorbox}
\tcbuselibrary{theorems, breakable}
\newtcbtheorem{example}{Example}%
{colback=gray!5,colframe=white!35!black,fonttitle=\bfseries, breakable}{th}
\newtcbtheorem{objectives}{Learning objectives}%
{colback=aux_green!5,colframe=white!35!aux_green,fonttitle=\bfseries, breakable}{th}

% Aliases and macros
\newcommand{\tr}[1]{{\mathrm{tr}}( #1 )}
\renewcommand{\arraystretch}{1.3}
\renewcommand{\abstractname}{General information}


\title{Structural Optimization}
\author{Nils Meyer}
\date{May 2023}

\begin{document}

\maketitle

\begin{abstract}
    This is the lecture manuscript for the course \emph{Structural optimization (MRM-0156)} held during the summer term 2023 at University of Augsburg. 

    Accompanying code to reproduce examples and figures may be found at \url{https://github.com/meyer-nils/structural_optimization}. This repository also stores solutions to the exercise tasks. Solving the exercises and examples on your own is vital to gather proper understanding of the presented topics. 

    Credits are assigned in an oral examination in combination with a semester task that has to be submitted prior to the examination. This task should demonstrate that you are capable to apply and extend methods of this course to a problem of your own choice. An example for a semester task would be an extension of the presented two-dimensional truss problems to three-dimensional problems. 

    This course is held for the first time in summer term 2023. Even though the manuscript was prepared with great care, it is likely that it still contains mistakes. If you find one or if you are in doubt, please don't hesitate to contact \href{mailto:nils.meyer@uni-a.de}{nils.meyer@uni-a.de}. 
\end{abstract}

\setcounter{tocdepth}{1}
\tableofcontents

\include{chapters/introduction}
\include{chapters/unconstrained_optimization}
\include{chapters/constrained optimization}
\include{chapters/approximation_optimization}
\include{chapters/sizing}
%\include{chapters/sensitivity}
%\include{chapters/continuum_mechanics}
\include{chapters/fem}
\include{chapters/topology}
\include{chapters/shape}
\include{chapters/composite}


\end{document}
